\documentclass[12pt , letterpaper]{article}

\usepackage{xcolor}
\usepackage[parfill]{parskip}
\usepackage{ragged2e}

%LaTeX knows that the doc is an article.

\begin{document}
\title{\LaTeX}
\author{Prateek Garg}
\maketitle

\textbf{This is me writing tex for first time}
\textit{hehe honestly.} 
\emph{ok}
\textsc{captilaised letteege}
\underline{this is underlined text.}
\textbf{\textit{ italics + bold}} \textcolor{blue}{whoowhoo}
%\color{violet}
This is written in yellow.\textcolor{black!70}{Do you like it now?}
\textcolor{black!30}{This is other shade of grey}
\textcolor{black}{ ok  last one.}
\textcolor[wave]{600}{ 600 nm light u see.}
\textcolor{blue!40!green!55!black}{ woah. can mix colors as well.}
\textcolor{-green}{ complement wtf}
here we are. violets are blue indeed.
{\tiny just like your pp}
{\small just like your balls.}
just like your dreams.
{\large :)}
{\huge just like :)}
\normalsize

\begin{center}
    center alignment using ragged2e package.

    dhvbdvhbdvbdcddcd
    chbdskhbsdkbvskhsbvkhbhvkhsbvkhsbvkhsdbvkbvkbsvfhvjfdvf
    vfbvhfbhvfbdhvfd ------------------- \\
    vfhvbfhvbf it works. yrt anotjrbgb way tp do this. \par
    vnhfyivbidfhvbhfdibvhdifbvidfbvifd.
    How to introducw vertical space in paras?

    \vspace{1.9em}
    vnfjvnfjnvf. \hspace{3.5em} hori space like this.

\end{center}

\raggedleft f breib rieubiuvb rebgiuerb my name is Prateek Garg.
cdc b hdsvudsgv   chdsv hudsvuvsdyvs
dknsdvbhj   svhs    b v
kvnd j vbjhd svh dsvhdsvhsdhvbsdkvbsjdvnds;
dvljbshvysdcuy w  e o a f ; o awebefotuaweitwe;fawg 
o88yfvere;uvser[hgputhoityj0ithpithbirtbgipuhhgurt 
hh98rty08-w4h9pywhgp9y9eiyogasukgfvddkjgvzd khlvboyfvlhsb;iuig
]. \par uihuibviffbvhifhbvkbld blblggblidgbihdh obhgg
bvohbdvd;fg bklgkbkhbhkbdkbdlhdbl
nkgbkgbklfgb;fdbkb
gdgbfkb;bkgbgsgsdlifhgbsdfgfb
gnkjgd;og;jg

\raggedright fvfyayyyayayaya  yayay y  g g d  vd  s vs g  a dvkvosfvh v f o f y y v g  d o i y f g v od  d f y g v i y o d i g  v d i o y f  g o y i d f g v    f v d h f b v d f  v d h s f v b s f d v h d f b d f h b v d f b v fdb

vdfvhdfbfdbvdhfsbvsd
fhbdfhvbdfsvdfvdfiusvipus huhovoiyvhbihisebvo8y8 uboy 
uh uogv uog ugtuogvk siehirbviydsfvpiffdiuiuh

\justifying
vfvgdvgdfvjv vfhdvshfhf vdsbdcd sc
dsd ddd ddd dddd ddddd d ddddd   dd  d  dd  ddd
dddd ddd ddd dddd ddd ddd dd  ddd   d   d ddd  dddddd ddddd
ddddd dd d ddd dddd d ddddd  ddddd ddddd  
  ddddd  d dd      dd ddddd  d ddddd  ddddd  ddd  ddddd      ddddd 
 ddddd  d d dd  dd dddd   
 dddd ddd ddd dd  dddd  d dddd ddd   d  dd d  d 
hfbhb  vfhb vfhb dhfshv bh fdbvhd fbhfdb  fdhbvh     bf
 
\setlength{\parindent}{7em}
vhvjbdfhbvhfdbvdsfh vb   d fhbd h f  b vh f d b h d f v h b d s f v 
 v  jf k j v d f l v b d f k v b d f b v k d f

fvfdbvfdjhvfhdbvfhdbvhdfbvhdbvd]

\setlength{\parindent}{1em}
njfvhkdkbvhfbvhs

\begin{itemize}
    \item that is a list
    \item fvfdbvfdjhvfhdbvfhdbvhdfbvhdbvdvfvdvf
    \item vfvgdvgdfvjv
    \item fvfdbvfdjhvfhdbvfhdbvhdfbvhdbvdvfvfdvdfvfdv
    \begin{itemize}
        \item that is a list
        \item fvfdbvfd
        \item vfvgdvgdfvjv
        \item fvf
    \end{itemize}
\end{itemize}

\begin{enumerate}
    \item dcdcddcd
    \item cdcdcsdcsd
    \begin{enumerate}
        \item eecece
        \item ceeecece
        \item ceeececece
        \begin{itemize}
            \item dcdf df dhfshvf 
            \item  df 
            \item df 
            \item dhfshv df fdb 
            \item df d
        \end{itemize}
    \end{enumerate}
\end{enumerate}

\begin{description}
    \item[gvg] ghvgvgvgv
    \item[nkjknj] ikjoijoino]   
\end{description}

\end{document}
